Automated Topic Naming

### 2012-01-19 ese/ese.tex
edits before class

\section{Introduction}
A key problem for practicing software maintainers is gaining an
understanding of \emph{why} a system has evolved the way it has \cite{Mockus00}. 
This is different from \emph{how} a system has evolved. 
% NE this phrase confuses me: "because the change of behaviour itself is the \emph{how}.
Looking back on streams of artifacts scattered across different
repositories, inferring what activities were performed, when, and for
what reasons, is hard without expert advice from the developers
involved. 
%new stuff
% edit this. awkward
In this work we provide a method of automatically labelling  development topics extracted from commit logs called \emph{labelled topic extraction}.

@@

%migod
In general, the fruits of mining software artifacts are often project
specific and hard to generalize.  
However, in our previous work we
investigated \emph{topic trends} --- that is, topics that recur over
time --- we observed that topic trends often corresponded to
non-functional requirements (NFRs)~\cite{Hindle09ICSM}, which is
further emphasized in this paper due to the large numbers of NFR
labelled topics.  
This is encouraging, as NFRs have the property of being cross-domain
and widely applicable. 
In this sense, they are useful abstractions for developer
conversations about different software projects.  
Furthermore, there is a series of standards on NFRs, such as ISO9126 \cite{iso9126}, that are specifically intended to apply to projects of varying
types; this suggests that our goal of trying to extract NFR-related development topics, such as those related to software quality models, holds promise.

@@

This work extends our previous work~\cite{msr2011}. The major extensions in this paper are as follows:
\begin{itemize}
	%\item We added new results on developer activities.
	\item We conducted another case-study on PostgreSQL. 
	\item We used two authors to each annotate the same PostgreSQL topics in order to compare
these annotations. 
	\item We used this new case-study to test inter-rater reliability, described in Section \ref{sec:inter-rater}. 
	\item We conducted an analysis of PostgreSQL authors and their association with NFRs and
topics (Section \ref{sec:developers}).
\end{itemize}

@@

%Massey~\cite{massey02icse} and Scacchi~\cite{scacchi02,scacchi05b} looked at the topic of requirements in open-source software. 
% this reduces the line length and drops a ref even though we still have a scacchi kickin around
Massey~\cite{massey02icse} and Scacchi~\cite{scacchi05b} looked at the topic of requirements in open-source software. 
Their work discusses the source of the requirements and how they are used in the development process. 
 German~\cite{german03gnome} looked at GNOME specifically, and listed several sources for requirements: leader interest, mimicry, brainstorming, and prototypes. 
None of this work  addressed quality requirements in OSS, nor did it examine requirements trends.
% NE 0113 this seems too early to mention 'result'.
In Hindle et al. \cite{Hindle2007} we examined release patterns in OSS. That work showed that there is a difference between projects regarding maintenance
techniques. This supports the result described in this paper, that software qualities are not discussed with the same frequency across projects.

>>>>

\section{Introduction}
A key problem for practicing software maintainers is gaining an
understanding of \emph{why} a system has evolved the way it has \cite{Mockus00}. 
This is different from \emph{how} a system has evolved. 
% NE this phrase confuses me: "because the change of behaviour itself is the \emph{how}.
Looking back on streams of artifacts scattered across different
repositories, inferring what activities were performed, when, and for
what reasons, is hard without expert advice from the developers
involved. 
%new stuff
% edit this. awkward
In this work we provide a method of automatically labelling
development topics extracted from commit logs, this method is called \emph{labelled topic extraction}.

@@

%migod
In general, the fruits of mining software artifacts are often project
specific and hard to generalize.  
However, in our previous work we
investigated \emph{topic trends} --- that is, topics that recur over
time --- we observed that topic trends often corresponded to
\emph{non-functional requirements} (NFRs)~\cite{Hindle09ICSM}, which is
further emphasized in this paper due to the large numbers of NFR
labelled topics.  
This is encouraging, as NFRs have the property of being cross-domain
and widely applicable. 
In this sense, they are useful abstractions for developer
conversations about different software projects.  
Furthermore, there is a series of standards on NFRs, such as ISO9126 \cite{iso9126}, that are specifically intended to apply to projects of varying
types; this suggests that our goal of trying to extract NFR-related development topics, such as those related to software quality models, holds promise.

@@

This work extends our previous work~\cite{msr2011}. The major extensions in this paper are as follows:
\begin{itemize}
	%\item We added new results on developer activities.
	\item We conducted another case-study on PostgreSQL. 
	\item We used two authors to each annotate the same PostgreSQL topics in order to compare
these annotations. 
	\item We used this new case-study to test \emph{inter-rater
          reliability} (IRR), described in Section \ref{sec:inter-rater}. 
	\item We conducted an analysis of PostgreSQL authors and their association with NFRs and
topics (Section \ref{sec:developers}).
\end{itemize}

@@

%Massey~\cite{massey02icse} and Scacchi~\cite{scacchi02,scacchi05b} looked at the topic of requirements in open-source software. 
% this reduces the line length and drops a ref even though we still have a scacchi kickin around
Massey~\cite{massey02icse} and Scacchi~\cite{scacchi05b} looked at the topic of requirements in open-source software. 
Their work discusses the source of the requirements and how they are used in the development process. 
 German~\cite{german03gnome} looked at GNOME specifically, and listed several sources for requirements: leader interest, mimicry, brainstorming, and prototypes. 
None of this work  addressed quality requirements in OSS, nor did it examine requirements trends.
% NE 0113 this seems too early to mention 'result'.
In Hindle et al.~\cite{Hindle2007} we examined release patterns in OSS. That work showed that there is a difference between projects regarding maintenance
techniques. This supports the result described in this paper, that software qualities are not discussed with the same frequency across projects.
